LAGOS lake depth

### 2023-04-04 README.Rmd
full citation
hyphen fix
try manual meta tags

---
output: github_document
---

@@

**Stachelek J.**, P. J. Hanly, P. A., Soranno. Accepted. Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth. Inland Waters. doi:10.1080/20442041.2021.2006553

>>>>

---
output: github_document
header-includes:
  - <meta name="citation_author" content="Stachelek, Jemma">
  - <meta name="citation_publication_date" content="2022">
  - <meta name="citation_title" content="Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth">
  - <meta name="citation_pdf_url" content="https://github.com/cont-limno/bathymetry/raw/master/manuscript/manuscript.pdf">
---

@@

**Stachelek, J.**, Hanly, P.J., Soranno, P.A., 2022. Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth. Inland Waters, 12(2), 283-293.
10.1080/20442041.2021.2006553
